---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# reprep

<!-- badges: start -->
<!-- badges: end -->

reprep helps automate the creation of a **rep**etitive **rep**orting package.

## Installation

Install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("sharlagelfand/reprep")
```

## Usage

`reprep` functions are wrappers for [`usethis` package](https://github.com/r-lib/usethis) functions and as such, also operate on the active project. If you used `reprep` to create a new package, that is the active project.

The following shows how `reprep` can help create your own package for repetitive reporting.

```{r}
# Create a new package ---------------------------------------------------------
reprep::reprep("~/ttcreport/")
```

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = "~/ttcreport/")
```

```{r}
# Add a step to the package ----------------------------------------------------
# (e.g. querying data, cleaning data, report writeup)
reprep::step("query_data")
```
